Missing the Point: Non-Convergence in Iterative Imputation Algorithms

### 2020-04-28 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Plot labels

---
title: "Missing the Point: Non-Convergence in Iterative Imputation Algorithms"
runninghead: Oberman
author:
  name: H. I. Oberman
  num: 1
address:
  num: 1
  org: Department of Methodology and Statistics, Utrecht University, Utrecht, The Netherlands
corrauth: "Hanne Oberman, Sjoerd Groenman building, Utrecht Science Park, Utrecht, The Netherlands."
email: h.i.oberman@uu.nl
abstract: "Iterative imputation is a popular tool to accommodate missing data. While it is widely accepted that valid inferences can be obtained with this technique, these inferences all rely on algorithmic convergence. There is no consensus on how to evaluate the convergence properties of the method. This paper provides insight into identifying non-convergence of iterative impuation algorithms."
keywords: iterative imputation; non-convergence; mice
classoption:
 - Royal
 - times
bibliography: thesis.bib
bibliographystyle: sageh
output:
 rticles::sage_article:
  keep_tex: yes
---

@@

>>>>

---
title: "Missing the Point: Non-Convergence in Iterative Imputation Algorithms"
runninghead: Oberman
author:
  name: H. I. Oberman
  num: 1
address:
  num: 1
  org: Department of Methodology and Statistics, Utrecht University, Utrecht, The Netherlands
corrauth: "Hanne Oberman, Sjoerd Groenman building, Utrecht Science Park, Utrecht, The Netherlands."
email: h.i.oberman@uu.nl
abstract: "Iterative imputation is a popular tool to accommodate missing data. While it is widely accepted that valid inferences can be obtained with this technique, these inferences all rely on algorithmic convergence. There is no consensus on how to evaluate the convergence properties of the method. This paper provides insight into identifying non-convergence of iterative impuation algorithms."
keywords: Iterative imputation; non-convergence; mice
classoption:
 - Royal
 - times
bibliography: thesis.bib
bibliographystyle: sageh
output:
 rticles::sage_article:
  keep_tex: yes
---

@@

# Grading

Scientific contribution
(clear research question, convincing argumentation that the study adds to the scientific literature)

Theory
(use of theory, clear hypotheses, relevant literature)

Method
(correct data collection/handling, measures, choice and description of method of analysis)

Results
(correct interpretation of findings, clear presentation)
Discussion and conclusions
(summary, broader implications, limitations, future research)

Written presentation
(writing, structure, tables and figures, references)

### 2020-04-28 3.Thesis/1.SimulationStudy/Writeup/manuscript.tex
Plot labels

\keywords{iterative imputation; non-convergence; mice}

@@

>>>>

\keywords{Iterative imputation; non-convergence; mice}

@@

\hypertarget{grading}{%
\section{Grading}\label{grading}}

Scientific contribution (clear research question, convincing
argumentation that the study adds to the scientific literature)

Theory (use of theory, clear hypotheses, relevant literature)

Method (correct data collection/handling, measures, choice and
description of method of analysis)

Results (correct interpretation of findings, clear presentation)
Discussion and conclusions (summary, broader implications, limitations,
future research)

Written presentation (writing, structure, tables and figures,
references)
